---
title: "Usage Examples for navr"
author: "Kenton Russell"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Usage Examples for navr}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r echo = F}
### get knitr just the way we like it

knitr::opts_chunk$set(
  message = FALSE
  , warning = FALSE
  , error = FALSE
  , tidy = FALSE
  , cache = FALSE
  #, results = 'asis'
)
```

### Getting Started
`navr` has not achieved CRAN status yet, so for now we will install with `devtools::install_github` as shown in the code below.

```{r eval = F}
devtools::install_github("timelyportfolio/navr")
```

### Simple Example

```{r}
library(navr)
library(htmltools)

# navr loves htmltools::tags, and I do too
#   so let's use them

tagList(
  tags$div(
    id = "simple-toolbar"
    ,style="width:100%;height:300px;border: dashed 0.2em lightgray;"
    ,tags$h1( "Div in Need of Toolbar" )
    ,tags$p( "If all goes well, you should see something that resembles a toolbar.
      This toolbar is built in R using the htmlwidget "
      , tags$a(tags$code("navr"),href = "https://github.com/timelyportfolio/navr")
      ," which wraps the tiny, dependency-free powerhouse "
      ,tags$a(tags$code("responsive-nav.js"),href = "http://responsive-nav.com/")
      ,".  Isn't open source great?  For bonus points, open this in a mobile device"
      ,"or make your screen small enough to see the hamburger icon"
      , tags$span( class="fa fa-bars" )
      ,"."
    )
  )
  ,navr(
    "#simple-toolbar"  # id of selector for the div above
    ,tagList(
      tags$ul(style = "float:left;"
        ,tags$li(tags$a("worthless1"),href="")  # for now just text
        ,tags$li(tags$a("worthless2"),href="") # for now just text
      )
    )
    , options = list( insert = "after" )
  )
)

```

### `htmlwidget` Example

I can imagine a scenario where one of our `htmlwidget` friends might need a toolbar.  Let's say a
`DiagrammeR` diagram wants to add a toolbar for exporting the rendered SVG.  We could do something like this.

```{r}
library(DiagrammeR)

gV <- grViz(
  "digraph{ DiagrammeR -> HTML; navr -> HTML; HTML -> beautiful; }"
  , height = 400, width = 600
)

tagList(
  # wrap diagram in a div since a lot of htmlwidgets clear contents
  tags$div(id = "diagram-needs-toolbar"
    ,gV
  )
  ,navr(
    selector = "#diagram-needs-toolbar"
    # use HTML instead of tags
    ,taglist = HTML("
      <ul>
        <li><a onclick = 'exportSVG()' href = '#diagram-needs-toolbar'>Export to SVG</a></li>
      </ul>
    "
    )
  )
  ,tags$script("
    function exportSVG(){
      window.open(
        [
          'data:;base64,',
          window.btoa((new XMLSerializer()).serializeToString(
              document.getElementById('diagram-needs-toolbar')
                .getElementsByTagName('svg')[0]
          ))
        ].join('')
      )
    }
  ")
)
```


### Stylish Hover Effects
We can apply these stylish [hover effects](http://ianlunn.github.io/Hover/) from [Ian Lunn](https://github.com/IanLunn) with the helper function `add_hover`.  There are lots of different effects.  Let's try `pop` and `float`.

```{r}
library(htmltools)
library(navr)

# build a simple nav
n1 <- navr(
  selector = "#pop-toolbar"
  ,taglist = tagList(
    tags$ul(
      tags$li(style="border: solid 0.1em white;","Popper")
      ,tags$li(style="border: solid 0.1em white;","Popping")
    )
  )
)
# make a copy to show another effect
n2 <- n1
n2$x$taglist = tagList(
  tags$ul(
    tags$li(style="border: solid 0.1em white;","Floater")
    ,tags$li(style="border: solid 0.1em white;","Floating")
  )
)


tagList(
  tags$div(
    id = "pop-toolbar"
    ,style="width:300px;height:300px;border: dashed 0.2em lightgray;"
    ,tags$h3("Hover Effects")
    ,"Hover effects are nice and let our users know that our
      navr actually does something.  Just wait until you see our navr with icons."
  )
  ,add_hover(n1,"pop")
  ,add_hover(n2,"float")
)
```

### Awesome Font-Awesome Icons

Font-Awesome are the nice open-source MIT-licensed icons in Bootstrap.  `add_font` makes it easy to use these icons in our toolbar.  Even neater, the hover effects shown below play very nicely with Font-Awesome, so I would encourage `add_hover` + `add_font_awesome`.  *If you're in shiny, no need to use `add_font_awesome` since Bootstrap already gives you these icons.*

```{r}
library(htmltools)
library(navr)

# build a simple nav
n1 <- navr(
  selector = "#icon-toolbar"
  ,taglist = tagList(
    tags$ul(style="line-height:120px; text-align:center; vertical-align:middle;"
      ,tags$li(
        style="border: solid 0.1em white;border-radius:100%;line-height:inherit;width:130px;height:130px;"
        , class="fa fa-beer fa-4x"
      )
      ,tags$li(
        style="border: solid 0.1em white;border-radius:100%;line-height:inherit;width:130px;height:130px;"
        , class="fa fa-bell fa-4x"
      )
    )
  )
)

tagList(
  tags$div(
    id = "icon-toolbar"
    ,style="width:300px;height:300px;border: dashed 0.2em lightgray; float:left;"
    ,tags$h3("Icon with Hover Effects")
    ,"Hover effects are even nicer when they work with icons, especially our easy
    to add Font-Awesome icons."
  )
  ,add_hover(add_font_awesome(n1),"fade")
)
```

### navr + sortableR

I bet last week's widget `sortableR` will also work with `navr`.

```{r}
library(navr)
library(sortableR)
library(htmltools)

# build a simple nav
n1 <- navr(
  selector = "#sortableR-toolbar"
  ,taglist = tagList(
    tags$ul(id = "sort-navr"
      ,style="line-height:120px; text-align:center; vertical-align:middle;"
      ,tags$li(
        style="border: solid 0.1em white;border-radius:100%;line-height:inherit;width:130px;height:130px;"
        , class="fa fa-bug fa-4x"
      )
      ,tags$li(
        style="border: solid 0.1em white;border-radius:100%;line-height:inherit;width:130px;height:130px;"
        , class="fa fa-binoculars fa-4x"
      )
      ,tags$li(
        style="border: solid 0.1em white;border-radius:100%;line-height:inherit;width:130px;height:130px;"
        , class="fa fa-camera fa-4x"
      )
      ,tags$li(
        style="border: solid 0.1em white;border-radius:100%;line-height:inherit;width:130px;height:130px;"
        , class="fa fa-briefcase fa-4x"
      )
    )
  )
)

tagList(
  tags$div(
    id = "sortableR-toolbar"
    ,style="width:300px;border: dashed 0.2em lightgray; float:left;"
    ,tags$h3("sortableR Icons")
    ,"If you don't like the order of these icons, change them by drag and dropping."
  )
  ,add_font_awesome(n1)
  ,sortableR("sort-navr")
)
```
